Title

### 2013-03-22 inc/gun/gun_design.tex
move FEM data from figure in acc model to acc design and forward reference to it

As derived in Section \ref{sec:gun_model}, the change of electric field strength near the anode will cause some divergence of the electic field.
This field will cause a divergence of the beam.
Future work will include investigating the designs of Butler %TODO reference
which may be able to build in an intrinsic lensing to compensate for this effect.

>>>>

\begin{figure}
  \centering

  \begin{tikzpicture}
    \input{onaxis_FEM}
  \end{tikzpicture}

  \caption[An example of a tanh form acceleration region for three different ``sharpness'' values]{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values, the same data as in \ref{fig:gun-sharpness}\subref{fig:field_on_axis}.
    The square data points represent the on-axis electric field data from FEM simulations.
  }
  \label{fig:field_on_axis_fem}
\end{figure}

\ref{fig:field_on_axis_fem} compares the FEM computed electric field to the assumed model form (\label{eq:anode_tanh}) for several values of the sharpness parameter $s$; the lines are the same as in \ref{fig:gun-sharpness}\subref{fig:field_on_axis}.
As derived in Section \ref{sec:gun_model}, the change of electric field strength near the anode will cause some divergence of the electic field.
This field will cause a divergence of the beam.
Future work will include investigating the designs of Butler %TODO reference
which may be able to build in an intrinsic lensing to compensate for this effect.

### 2013-03-22 inc/gun/gun_model.tex
move FEM data from figure in acc model to acc design and forward reference to it

We may choose to assume that the on-axis field is defined as a smoothed step down function
\begin{equation} \label{eq:anode_tanh}
  F_z(0,z^{\prime}) = \frac{eV}{2z^{\prime}_A} \left( 1 - \tanh \left( \frac{ z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \right)
\end{equation}
where $V$ is the accelerating potential, $z^{\prime}_A$ is the position of the anode (the cathode assumed to be at $z^{\prime} = 0$) and $s$ is a constant quantifying the ``sharpness'' of the fall-off of the electric field.
Indeed, this form is analgous to the super-Gaussian envalope (\ref{eq:reg_of_influence}), however it is open ended on the cathode side, which is necessary for the electrons to be accelerated away from the photocathode.
Given this form (demonstrated in Section \ref{sec:gun_design}) the ``lensing'' strengths are then
\begin{gather}
  M_{\smallT} = -\frac{eVs}{4z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \\
  M_z = \frac{eVs}{2z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \, \text{.}
\end{gather}
As with the RF cavity, one needs to include the on-axis force (\ref{eq:anode_tanh}) in the overall pulse propagation kinematics.

\begin{figure}
  \centerline{
    \subfloat[][]{
      \label{fig:field_on_axis}
      \input{onaxis}
    }
    \subfloat[][]{
      \label{fig:tanh_sharpness}
      \input{sharpness}
    }
  }
  \caption[An example of a tanh form acceleration region for three different ``sharpness'' values]{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values.
    The square data points in \protect\subref{fig:field_on_axis} represent the on-axis electric field data from FEM simulations, see Section \ref{sec:gun_design}.
    The colored electric fields in figure \protect\subref{fig:field_on_axis} correspond to the pulse width (solid) and length (dashed) in figure \protect\subref{fig:tanh_sharpness}.
  }
  \label{fig:gun-sharpness}
\end{figure}

\ref{fig:gun-sharpness} shows an example acceleration region for three values of the ``sharpness'' $s$ as well as longitudinal FEM field data which is explained further in Section \ref{sec:gun_design}.
%TODO possibly remove the FEM data? it doesn't help much here and is confusing since it hasn't been introduced
What is clear from this figure is that the dynamics are not highly coupled to the value of this hard-to-quantify parameter.
For all values of $s$ the divergence of the beam is equal (though the size may vary slightly).
Interestingly the length of the pulse is stabilized on exiting the anode, coming very nearly to a constant length (not expanding nor contracting).
This effect is due to the slower electrons remaining in the cavity longer and thus receiving an additional kick, as described in \cite{oudheusden_electron_2007}.

>>>>

We may choose to assume that the on-axis field is defined as a smoothed step down function
\begin{equation} \label{eq:anode_tanh}
  F_z(0,z^{\prime}) = \frac{eV}{2z^{\prime}_A} \left( 1 - \tanh \left( \frac{ z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \right)
\end{equation}
where $V$ is the accelerating potential, $z^{\prime}_A$ is the position of the anode (the cathode assumed to be at $z^{\prime} = 0$) and $s$ is a constant quantifying the ``sharpness'' of the fall-off of the electric field.
Indeed, this form is analgous to the super-Gaussian envalope (\ref{eq:reg_of_influence}), however it is open ended on the cathode side, which is necessary for the electrons to be accelerated away from the photocathode.
Given this form the ``lensing'' strengths are then
\begin{gather}
  M_{\smallT} = -\frac{eVs}{4z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \\
  M_z = \frac{eVs}{2z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \, \text{.}
\end{gather}
As with the RF cavity, one needs to include the on-axis force (\ref{eq:anode_tanh}) in the overall pulse propagation kinematics.

\begin{figure}
  \centerline{
    \subfloat[][]{
      \label{fig:field_on_axis}
      \begin{tikzpicture}
        \input{onaxis}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:tanh_sharpness}
      \input{sharpness}
    }
  }
  \caption[An example of a tanh form acceleration region for three different ``sharpness'' values]{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values.
    The colored electric fields in figure \protect\subref{fig:field_on_axis} correspond to the pulse width (solid) and length (dashed) in figure \protect\subref{fig:tanh_sharpness}.
    This form is compared to FEM simulated electric field data in \ref{fig:field_on_axis_fem}.
  }
  \label{fig:gun-sharpness}
\end{figure}

\ref{fig:gun-sharpness} shows an example acceleration region for three values of the ``sharpness'' $s$.
What is clear from this figure is that the dynamics are not highly coupled to the value of this hard-to-quantify parameter.
For all values of $s$ the divergence of the beam is equal (though the size may vary slightly).
Interestingly the length of the pulse is stabilized on exiting the anode, coming very nearly to a constant length (not expanding nor contracting).
This effect is due to the slower electrons remaining in the cavity longer and thus receiving an additional kick, as described in \cite{oudheusden_electron_2007}.
This longitudinal electric field shape is compared to the electric field computed by finite-element (FEM) simulations of our acceleration cavity in Section \ref{sec:gun_design}.
